---
title: "Blog Dominican Republic"
site: distill::distill_website
listing: posts
output: html_document
---

# Data Description

This dataset are about confirmed,death and recovered cases in Dominican Republic during January 2020 to August 2021,which recorded the daily increased number of cases out of total population.And also contain the accumulated number of Dominican people who have vaccinated from February 2021 to  August 2021,which includes number of people who partially vaccinated,number of people who fully vaccinated and total doses of vaccination .The data was provided through multiple Covid19-relevant source includes World Health Organization (WHO),DXY.cn. Pneumonia. 2020,and Colorado,the website of mentioned source will be given at the end of blog.

# Table Presentation
```{r echo = FALSE,message=FALSE,warning=FALSE}

knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning=FALSE,options(scipen=200))

library(tidyverse)
library(kableExtra)
library(gt)
library(DT)

```


```{r}
case_data<-read.csv("data/coronavirus.csv")%>%
  filter(country =="Dominican Republic")%>%
  select("date",
         "country",
         "type",
         "cases")%>%
  separate(col= date,
           into = c("year","month","day")
           , "-")%>%
  group_by(type,
           year,
           month)%>%
  summarise(monthly_cases=sum(cases))%>%
  unite("time", year, month,sep='-')

case_data_wider<-case_data%>%
  pivot_wider(id_cols = time,
              names_from = type,
              values_from = monthly_cases)
```


```{r}

vaccine_data<-read.csv("data/covid19_vaccine.csv")%>%
  filter(country_region =="Dominican Republic")%>%
  select(2:5)%>%
  filter(date %in% c("2/15/2021",
                     "2/28/2021",
                     "3/15/2021",
                     "3/30/2021",
                     "4/15/2021",
                     "4/30/2021",
                     "5/15/2021",
                     "5/30/2021",
                     "6/15/2021",
                     "6/30/2021",
                     "7/15/2021",
                     "7/30/2021",
                     "8/15/2021",
                     "8/30/2021"
                     ))%>%
  mutate("Fully vaccinated rate" = people_fully_vaccinated/10627200)

```

```{r}

 case_data_wider%>%DT::datatable(
          escape = FALSE,
          class = 'cell-border stripe',
          options = list(pageLength = 6),
          caption = 'The Covid19 Cases in Dominican Republic',
          filter = 'top',
          colnames = c('Time', 'Confirmed', 'Death', 'Recovered'))



```
 
(tips:There is suppose to have a interactive DT table,but due to certain unknown technical issues my R studio can not output the outcome of code on HTML,but the DT table dose exist in the Rmd file.I have pose this issue on discussion forum but it is a little bit of late.You can check in the Rmd file.)

```{r}

gt(vaccine_data) %>% 
  tab_header(title = "Number of Vaccinated People in Dominican Republic(Accumulated)",
             subtitle = "Data collected monthly from February to August 2021") %>% 
  tab_source_note(md("Source: https://github.com/RamiKrispin/coronavirus")) %>% 
  cols_label(
    date = html("Date"),
    doses_admin = html("Doses_admin"),
    people_partially_vaccinated = html("Partially_vaccinated"),
    people_fully_vaccinated = html("Fully_vaccinated")
  )



```

From the table "Number of Vaccinated People in Dominican Republic(Accumulated)",the number of Dominican people has been vaccinated was increased significantly in the passed half year,meanwhile the number of death and confirmed cases has drop to a really low level.That means vast number of vaccination is effective,but by the end of August,the total vaccinated rate of population of Dominican Republic is 43.56%, which is not sufficiently high to achieve the 85% majority immunity for 10627200 of Dominican people.

```{css}

table, th, td
{
    border: 1px solid grey;
}

th
{
    background-color:green;
    color:white;
}

  
  
gt_title {
    color:yellow;
    font-size: 125%;
    font-weight: initial;
    padding-top: 4px;
    padding-bottom: 4px;
    border-bottom-color: green;
    border-bottom-width: 2;
} 
```


```{r}
vaccine_data2<-read.csv("data/covid19_vaccine.csv")%>%
  filter(country_region =="Dominican Republic")%>%
  select(2:5)%>%
  filter(date %in% c("2/28/2021",
                     "3/30/2021",
                     "4/30/2021",
                     "5/30/2021",
                     "6/30/2021",
                     "7/30/2021",
                     "8/30/2021"
                     ))%>%
  pivot_longer(cols = -date,
               names_to = "Type",
               values_to = "cases")%>%
  pivot_wider(id_cols = Type,
              names_from = date,
              values_from = cases)%>%
  rename(Februray="2/28/2021",
         March="3/30/2021",
         April="4/30/2021",
         May="5/30/2021",
         June="6/30/2021",
         July="7/30/2021",
         August ="8/30/2021")%>%
  mutate('2021-03'=March-Februray,
         "2021-04"=April-March,
         "2021-05"=May-April,
         "2021-06"=June-May,
         "2021-07"=July-June,
         "2021-08"=August-July)%>%
  select(Type,
         9:14)%>%
  pivot_longer(cols = -Type,
               names_to = "time",
               values_to = "vaccinated_people")%>%
  pivot_wider(id_cols = time,
              names_from = Type,
              values_from = vaccinated_people)
```


```{r}
lm_data<-left_join(case_data_wider,vaccine_data2,by="time")%>%
  filter(time %in% c("2021-03",
                   "2021-04",
                   "2021-05",
                   "2021-06",
                   "2021-07",
                   "2021-08"))%>%
  mutate('Confirmed_rate'= confirmed/10627200,
         'Death_rate'= death/10627200,
         'Recovered_rate'= recovered/10627200,
         'Confirmed_rate'= confirmed/10627200,
         'Monthly_fully_vaccinated_rate'= people_fully_vaccinated/10627200,
         )

m <- lm(Monthly_fully_vaccinated_rate ~  Confirmed_rate + Death_rate + Recovered_rate, data = lm_data)
d <- coef(summary(m))
knitr::kable(d, booktabs = TRUE, caption = 'The estimated linear model for the vaccination rate')%>%
  kable_styling(c("basic",
                  fixed_thead = TRUE),
                latex_options = "HOLD_position")

```

# Sources

Colorado at: <https://covid19.colorado.gov/data)>

World Health Organization (WHO) at: <https://www.who.int/>

DXY.cn. Pneumonia. 2020. at: <https://ncov.dxy.cn/ncovh5/view/pneumonia.>